An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-05 scagnostics.Rmd
Adding density plots for index distribution.

>>>>

## Distributions of index values

Compare typical index values over the two tour paths. Notation: path1 / 2 labels tour from V1-V2 to V3-V4 / V5-V6.

```{r indexDist, fig.width=6, fig.height=7, fig.cap="Short tour paths with scagnostics computed on projections. Most of the indices exhibit sharp jumps in scagnostic value."}
fullResMelt1 <- fullResMelt %>% add_column(path="path1")
fullResMeltPlanned1 <- fullResMeltPlanned %>% add_column(path="path2")
allRes <- rbind(fullResMelt1, fullResMeltPlanned1)
ggplot(allRes, aes(x=value)) +
  geom_density(aes(color=path, linetype = factor(size))) +
  facet_wrap(variable~name, ncol=3, scales = "free_y", labeller = label_wrap_gen(multi_line=FALSE))
```
